---
title: "About this site"
---
<center>
<button> <a href="https://www.coris.noaa.gov/monitoring/" target="_blank" style="font-size:100%;color:#2471A3;font-weight:bold"> NCRMP Website</a></button>
</center>
<br>


## What do I need to download? {.tabset}
### Benthic
The benthic R package can be accessed <a href="https://github.com/shgroves/NCRMP_benthics" target="_blank" style="color:blue">here.</a>
Instructions to download and install the package are available on the GitHub page. <br>
In addition to the R package, the files for the benthic figures are available under the tab "Download" individually or in a zip file.
<br><br><br>

### Fish
The fish R package can be accessed <a href="https://github.com/jeremiaheb/rvc" target="_blank" style="color:blue">here.</a>
Instructions to download and install the package are available on the GitHub page. <br>
In addition to the R package, the files for the benthic figures are available under the tab "Download" individually or in a zip file.
<br><br><br>


## Getting started

<br>

### Load libraries and scripts

Once you have downloaded/installed all relevant R scripts and packages, they must be loaded into R. <br>
To use load installed NCRMP libraries, use the following: <br>
Benthic: **library(ncrmp.benthics.analysis)** <br>
Fish: **library(rvc)**


#### How to source R files {.tabset}
To use the files downloaded here as .R scripts, use the following template: <br>
**source("path/to/file.R")**
<br>

##### Benthic files and libraries example
```{r Bsource, message=FALSE,warning=FALSE}
library(ncrmp.benthics.analysis)
library(tidyverse)
```

<br>

##### Fish files and libraries example
```{r Fsource, message=FALSE,warning=FALSE}
library(rvc)
library(tidyverse)
source("fish_plots/theme_publication.R")
source("fish_plots/labeler.R")
source("fish_plots/WrapperFunctions.R")
source("fish_plots/QL_binned_LengthFreq.R")
source("fish_plots/QL_SubregionDensityPlot.R")
source("fish_plots/plot_horizontal_bar_shared_axis.R")
```

<br>

### Load data {.tabset}

#### Benthic
Benthic data is downloaded with the package. <br>
ADD MORE HERE
<br><br>

#### Fish
Fish data is not included in the package download, and must be accessed from the server. <br>
Data can be accessed using the method **getRvcData()**. See example below: 
```{r fishdata, message=FALSE,warning=FALSE}
keys11_14 = getRvcData(years = 2011:2014, regions = c("FLA KEYS"))
torts12_16 = getRvcData(years = 2012:2016, regions = c("DRY TORT"))
```
<br><br>

## About the data 

<br>

### Benthic {.tabset}

#### Coral Species
BLAH BLAH

#### Regions
BLAH BLAH

<br>

### Fish {.tabset}

#### Fish Species
BLAH BLAH

#### Regions
BLAH BLAH