---
title: "Getting Started"
---

:::: {class='fluid-row'}

::: {class='col-md-3'}

<button> <a href="https://www.coris.noaa.gov/monitoring/" target="_blank" style="font-size:100%;color:#2471A3;font-weight:bold"> NCRMP Website</a></button>

<br>

<fieldset>
   <legend>Getting started checklist:</legend>
</fieldset>

### {.tabset}

#### Benthic

<fieldset>
   <label><input type="checkbox" name="pkg"> Package downloaded and installed</label><br />
   <label><input type="checkbox" name="load"> Package loaded into environment</label><br />
   <label><input type="checkbox" name="source"> R scripts sourced</label><br />
   <label><input type="checkbox" name="data"> Call data from package</label><br />
</fieldset>

#### Fish

<fieldset>
   <label><input type="checkbox" name="pkg"> Package installed</label><br />
   <label><input type="checkbox" name="load"> Package loaded into environment</label><br />
   <label><input type="checkbox" name="source"> R scripts sourced</label><br />
   <label><input type="checkbox" name="data"> Data loaded into object in environment</label><br />
</fieldset>

:::

::: {class='col-md-9'}

<!-- SIDE BAR ABOVE
REST OF PAGE BELOW -->

## What do I need to download? {.tabset}
### Benthic
The benthic R package can be accessed <a href="https://github.com/shgroves/NCRMP_benthics" target="_blank" style="color:blue">here.</a>
Instructions to download and install the package are available on the GitHub page. <br>
In addition to the R package, the files for the benthic figures are available under the tab "Download" individually or in a zip file. <br><br>

Download instructions: <br>
1. Download the .zip file from GitHub (green "Code" button, download zip) <br>
2. Open the .Rproj file inside the .zip in RStudio <br>
3. Run the following code
```{r eval=FALSE}
install.packages('devtools') #if devtools is not already installed
devtools::install()
```
<br>
4. Exit the .Rproj and run the following code from your own project or workspace
```{r eval=FALSE}
library(ncrmp.benthics.analysis) 
```


<br><br><br>

### Fish
The fish R package can be accessed <a href="https://github.com/jeremiaheb/rvc" target="_blank" style="color:blue">here.</a>
Instructions to download and install the package are available on the GitHub page. <br>
In addition to the R package, the files for the benthic figures are available under the tab "Download" individually or in a zip file. <br> <br>

Download instructions: <br>
1. Run the following code in R
```{r eval=FALSE}
install.packages('devtools') #skip if devtools is already installed
devtools::install_github('jeremiaheb/rvc')
```
There may be warnings about packages (such as RTools) that are not installed and are necessary for developing packages - this can be ignored or you can install the package if you so choose. 
<br><br><br>


## Getting started

<br>

### Load libraries and scripts

Once you have downloaded/installed all relevant R scripts and packages, they must be loaded into R. <br>
To use load installed NCRMP libraries, use the following: <br>
Benthic: **library(ncrmp.benthics.analysis)** <br>
Fish: **library(rvc)**
<br><br>

#### Working directories
You will want to make sure that you are working out of the same place on your computer as where you have stored all of the files downloaded from this site. If you aren't sure where your working directory is pointing, use the command **getwd()** in the console. Use **setwd()** to set a working directory [ex: **setwd("C:/Users/username/Desktop/NCRMP")**]. If you are using RStudio, you can set your working directory in the file viewer window under "More>Set As Working Directory".
<br><br>

#### How to source R files {.tabset}

<button> <a href="downloadpkgs.html" target="_self" style="font-size:100%;color:#2471A3;font-weight:bold"> Download scripts here</a></button>

To use the files downloaded here as .R scripts, use the following template: <br>
**source("path/to/file.R")** <br>
This will allow you to load the functions in the scripts for your own figures without running the code for each function individually in the console.
<br>

##### Benthic files and libraries example
```{r Bsource, message=FALSE,warning=FALSE}
library(ncrmp.benthics.analysis)
library(tidyverse)
source("benthic_plots/Benthic_Wrapper_functions.R")
```

<br>

##### Fish files and libraries example
```{r Fsource, message=FALSE,warning=FALSE}
library(rvc)
library(tidyverse)
source("fish_plots/theme_publication.R")
source("fish_plots/labeler.R")
source("fish_plots/WrapperFunctions.R")
source("fish_plots/QL_binned_LengthFreq.R")
source("fish_plots/QL_SubregionDensityPlot.R")
source("fish_plots/plot_horizontal_bar_shared_axis.R")
```

<br>

### Load data {.tabset}

#### Benthic
Benthic data is downloaded with the package. <br>
When data sets are added, the package must me re-installed.
<br><br>

#### Fish
Fish data is not included in the package download, and must be accessed from the server. <br>
Data can be accessed using the method **getRvcData()**. See example below: 
```{r fishdata, message=FALSE,warning=FALSE}
keys11_14 = getRvcData(years = 2011:2014, regions = c("FLA KEYS"))
torts12_16 = getRvcData(years = 2012:2016, regions = c("DRY TORT"))
```
When data sets are added, no additional actions must be taken. <br>

Below are the locations where fish data is provided. The code must be used when getting data from the server rather than the name.
```{r fishloc, message=FALSE,warning=FALSE, echo=FALSE}
library("DT")
data <- read.csv("fish_plots/NCRMP-f-loc.csv")
df <- data.frame(data)
datatable(df, class = 'cell-border stripe', 
          options = list(ordering=F), rownames = FALSE)
```
<br>
When loading data, you can retrieve data for multiple regions and years at once, but for many of the figures shown on this site, you will want to only grab data for one location at a time as shown above. It is much easier to work with data from one location at a time. 

<br><br>

## About the data 

### Benthic {.tabset}

#### Coral Species
<a href="benthic_plots/benthic_spp.txt" download style="color:blue">Download list of coral species</a>

#### Regions
TO BE ADDED
<br>

### Fish {.tabset}

#### Fish Species
<a href="fish_plots/fish_spp.txt" download style="color:blue">Download list of fish species</a>

#### Regions
<!-- 
To add to the table, edit the NCRMP-f-datayrs.csv
-->

```{r fish_reg2, echo=FALSE, messages=FALSE, warning=FALSE}
library("DT")
data <- read.csv("fish_plots/NCRMP-f-datayrs.csv", header = FALSE)
df <- data.frame(data[,-1], row.names = data[,1])
colnames(df) <- as.character(df[1,])
df <- df[-1,]
df <- data.frame(t(df))
datatable(df, class = 'cell-border stripe', 
          options = list(ordering=F, pageLength = 25))
```


:::

::::