---
title: "&nbsp;"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 3
    code_folding: hide
---

<style type="text/css">
.main-container {
  max-width: 90% !important;
  margin: auto;
}
</style>

# **Fish: Time series**
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE, message=FALSE,warning=FALSE,class.source = 'fold-show'}
library(rvc)
library(tidyverse)
source("fish_plots/theme_publication.R")
source("fish_plots/labeler.R")
source("fish_plots/WrapperFunctions.R")
source("fish_plots/QL_binned_LengthFreq.R")
source("fish_plots/QL_SubregionDensityPlot.R")
source("fish_plots/plot_horizontal_bar_shared_axis.R")
#this block is invisible
#add any sources or packages needed for figures below
```

<br>

<!-- 
All figures are made using the species Ocyurus chrysurus (OCY CHRY) 
-->

## Load data
```{r data, message=FALSE,warning=FALSE,class.source = 'fold-show'}
keys11_14 = getRvcData(years = 2011:2014, regions = c("FLA KEYS"))
torts12_16 = getRvcData(years = 2012:2016, regions = c("DRY TORT"))
```

<br>

## Plots

<!-- To add another figure set (the #s control the headers):
### Figure type title {.tabset}

#### Defaults
'''{r example, warning=FALSE,message=FALSE,error=FALSE,results='hold', fig.keep='all'}
  #include function call here - only include required parameters
  #be sure to list all parameters with descriptive comments
'''

#### Alt
'''{r example, warning=FALSE,message=FALSE,error=FALSE,results='hold', fig.keep='all'}
  #include function call here - include all parameters
  #be sure to list all parameters with descriptive comments
'''

Defaults and alt are not necessarily required, but please include at least 2 variations of the figure.

When the figure is added, save the image of one of the variations to the folder labeled "home-figs" and add it to the home page linking to the figure
-->

### Domain density by year {.tabset}
#### Defaults
```{r ddy.d, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_domain_den_by_year(dataset = keys11_14, 
                        species = "ocy chry", 
                        length = NULL, #only fish >= length parameter are plotted
                        title = NULL, #add a figure title
                        print_dataframe = FALSE) #prints data used for figure
```
<br><br>

#### Alt
```{r ddy.a, warning=FALSE,message=FALSE,error=FALSE,results='hold', fig.keep='all'}
plot_domain_den_by_year(dataset = keys11_14, 
                        species = "OCY CHRY",
                        length = 30, #30cm length at capture in Florida
                        title = expression(paste(italic("O. chrysurus"), #Allows scientific name to be italicized
                                                " >= 30cm in the Florida Keys")), 
                        print_dataframe = TRUE) #prints data used for figure
```
<br><br>


### Domain density by protected status {.tabset}
#### Defaults
```{r ddyp.d, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_domain_den_by_year_by_prot(dataset = keys11_14, 
                        species = "ocy chry",
                        length = NULL, #only fish >= length parameter are plotted
                        title = NULL, #add a figure title
                        print_dataframe = FALSE) #prints data used for figure
```
<br><br>

#### Alt
```{r ddyp.a, warning=FALSE,message=FALSE,error=FALSE,results='hold', fig.keep='all'}
plot_domain_den_by_year_by_prot(dataset = keys11_14, 
                        species = "OCY CHRY",
                        length = 30, #30cm length at capture in Florida
                        title = expression(paste(italic("O. chrysurus"), #Allows scientific name to be italicized
                                                " >=30cm in the Florida Keys")), 
                        print_dataframe = TRUE) #prints data used for figure
```
<br><br>


### Domain occurrences by year {.tabset}
#### Defaults
```{r doc.d, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_domain_occ_by_year(data = torts12_16, #required
                        species = "OCY CHRY", #required
                        length = NULL, #only fish >= length parameter are plotted
                        print_dataframe = FALSE, #prints data used for figure
                        title = NULL)#add a figure title
```
<br><br>

#### Alt
```{r doy.a, warning=FALSE,message=FALSE,error=FALSE,results='hold', fig.keep='all'}
plot_domain_occ_by_year(data = torts12_16, #required
                        species = "ocy chry", #required
                        print_dataframe = TRUE, #prints data used for figure
                        length = 30, #30cm length at capture in Florida
                        title = expression(paste(italic("O. chrysurus"), #Allows scientific name to be italicized
                                                " >= 30cm in the Dry Tortugas")))
```
<br><br>


### Domain occur. by protected status {.tabset}
#### Defaults
```{r doyp.d, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_domain_occ_by_year_by_prot(data = torts12_16, #required
                        species = "ocy chry", #required
                        length = NULL, #only fish >= length parameter are plotted
                        print_dataframe = FALSE, #prints data used for figure
                        title = NULL)#add a figure title
```
<br><br>

#### Alt
```{r doyp.a, warning=FALSE,message=FALSE,error=FALSE,results='hold', fig.keep='all'}
plot_domain_occ_by_year_by_prot(data = torts12_16, #required
                        species = "OCY CHRY", #required
                        length = NULL,
                        print_dataframe = TRUE, #prints data used for figure
                        title = expression(paste(italic("O. chrysurus"), #Allows scientific name to be italicized
                                                " in the Dry Tortugas")))
```
<br><br>


### Domain biomass by year {.tabset}
#### Defaults
```{r dby.d, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_domain_biomass_by_year(dataset = keys11_14, #required 
                            species = "ocy chry", #required
                            length = NULL, #only fish >= length parameter are plotted
                            title = NULL, #add a figure title
                            print_dataframe = NULL) #prints data used for figure
```
<br><br>

#### Alt
```{r dby.a, warning=FALSE,message=FALSE,error=FALSE,results='hold', fig.keep='all'}
plot_domain_biomass_by_year(dataset = keys11_14, #required 
                            species = "OCY CHRY", #required
                            length = NULL,
                            title = expression(paste(italic("O. chrysurus"), 
                                                " in the Florida Keys")),#Allows scientific name to be italicized
                            print_dataframe = TRUE) #prints data used for figure
```
<br><br>


### Domain biomass by prot. status {.tabset}
#### Defaults
```{r dbyp.d, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_domain_biomass_by_year_by_prot(dataset = keys11_14, #required 
                            species = "OCY CHRY", #required
                            title = NULL, #add a figure title
                            print_dataframe = NULL) #prints data used for figure
```
<br><br>

#### Alt
```{r dbyp.a, warning=FALSE,message=FALSE,error=FALSE,results='hold', fig.keep='all'}
plot_domain_biomass_by_year_by_prot(dataset = keys11_14, #required 
                            species = "ocy chry", #required
                            title = expression(paste(italic("O. chrysurus"), 
                                                " in the Florida Keys")),#Allows scientific name to be italicized
                            print_dataframe = TRUE) #prints data used for figure
```
<br><br>


### Stratum density by year {.tabset}
#### Defaults
```{r sdy.d, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_stratum_den_by_year(dataset = keys11_14, #required
                         species = "ocy chry", #required
                         length = NULL, #only fish >= length parameter are plotted
                         title = NULL, #add a figure title
                         print_dataframe = FALSE) #prints data used for figure
```
<br><br>

#### Alt
```{r sdy.a, warning=FALSE,message=FALSE,error=FALSE,results='hold', fig.keep='all'}
plot_stratum_den_by_year(dataset = keys11_14, #required
                         species = "OCY CHRY", #required
                         length = 30, #30cm length at capture in Florida
                         title = expression(paste(italic("O. chrysurus"), 
                                                " >= 30cm in the Florida Keys")), #Allows scientific name to be italicized 
                         print_dataframe = TRUE) #prints data used for figure
```
<br><br>


### Stratum occurrence by year {.tabset}
#### Defaults
```{r soy.d, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_stratum_occ_by_year(dataset = torts12_16, #required
                         species = "ocy chry", #required
                         length = NULL, #only fish >= length parameter are plotted
                         title = NULL, #add a figure title 
                         print_dataframe = FALSE)#prints data used for figure
```
<br><br>

#### Alt
```{r soy.a, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_stratum_den_by_year(dataset = torts12_16, #required
                         species = "OCY CHRY", #required
                         length = NULL,
                         title = expression(paste(italic("O. chrysurus"), 
                                                " in the Dry Tortugas")), #Allows scientific name to be italicized 
                         print_dataframe = TRUE)#prints data used for figure
```
<br><br>


### Stratum biomass by year {.tabset}
#### Defaults
```{r sby.d, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_stratum_biomass_by_year(dataset = keys11_14, #required
                         species = "OCY CHRY", #required
                         length = NULL, #only fish >= length parameter are plotted
                         title = NULL, #add a figure title 
                         print_dataframe = FALSE)#prints data used for figure
```
<br><br>

#### Alt
```{r sby.a, warning=FALSE,message=FALSE,error=FALSE,results='hide', fig.keep='all'}
plot_stratum_biomass_by_year(dataset = keys11_14, #required
                         species = "ocy chry", #required
                         length = 30, #30cm length at capture in Florida
                         title = expression(paste(italic("O. chrysurus"), 
                                                " >=30cm in the Florida Keys")),#Allows scientific name to be italicized 
                         print_dataframe = TRUE)#prints data used for figure
```
<br><br>